### 2018-07-02 Thesis/Parts/Abstract/Abstract.tex
UVA_template
Updated pdfs
Auto stash before merge of "master" and "origin/master"

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\fakeheader{Abstract}
Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain. Many studies have been done concerning the quality and application of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites. Giving promising results, the word embeddings have been studied and improved over recent years. However, these studies have been focused on generic texts, which are not limited to the characteristics of in-domain texts such as rare domain-specific words or have been focussed on small sets of academic texts. This research focusses on the quality and application of word embeddings on domain-specific texts, concerning a large corpus of 1.391.543 scientific articles which have been published in 2017.
\end{document}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
Over the last few years, word embeddings have taken a dominant position in the Information Retrieval domain. Many studies have been done concerning the quality and application of word embeddings on general texts, such as the Wikipedia corpus and comments on review websites. Giving promising results, the word embeddings have been studied and improved over recent years. However, these studies have been focused on generic texts, which are not limited to the characteristics of in-domain texts such as rare domain-specific words or have been focussed on small sets of academic texts. This research focusses on the quality and application of word embeddings on domain-specific texts, concerning a large corpus of 1.391.543 scientific articles which have been published in 2017.\\
\vspace*{\fill}
\\
We aim to have this thesis published in the proceedings of the 14th Asia Information Retrieval Societies (AIRS) Conference (\url{http://airs2018.org/site/page.aspx?pid=901&sid=1221&lang=en}). \textit{Paper submission deadline: 23 July 2018; Notification of acceptance: 27 August 2018}
\end{document}

### 2018-07-02 Thesis/Parts/Background/Background.tex
Auto stash before merge of "master" and "origin/master"

\subheader{Neural Network}
A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified working of a neural network and its basic application in IR.
Neural Networks are multi-layered computational software, based on matrix transformations, which tries to map input values to output values. This mapping uses a pre-defined amount of layers that modify the values through matrix transformations. Neural networks rely on training to create optimal values for these layers. The values in the layers are only changed at training time; high-quality training data is therefore essential for neural networks. Neural networks can be applied to many different tasks, as long as there is sufficient training data available. The training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result. Which is the result that is as close as possible to the given output for all input and output sets, without under performing on other sets\footnote{Having only good results for the training/validation set is know as overfitting. This means that the layer-values are fine-tuned to only perform (extremely) well on one set, while under performing on others}.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it. For example, given the sentence\\
\begin{center}
\textit{"The quick brown fox jumps over the lazy dog"}
\end{center}
the Neural Network can be trained to either predict the words around "jumps", which we refer to as context words (the, quick, brown, fox, over, the, lazy, dog). It can also predict the word "jumps", given the context words (the, quick, brown, fox, over, the, lazy, dog). This result in a matrix, a vector per word which is referred to as a word embedding. This embedding indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts. It is to be noted that the word embeddings are only able to represent word relatedness to the other words trained in the same run. Due to the random initialization of the initial values of the layers in the neural networks, neural networks do not produce every run the same results. Therefore, word embeddings from different runs of the same neural network cannot be compared.

@@

\subheader{Text analysis techniques}
To enable a computer to process text, for embedding creation or other tasks, the text has to be processed by an algorithm. In this research, we used embeddings created by Word2Vec and TF-IDF feature vectors.
\begin{jumpin}
\subsubheader{Word2Vec}
Word2vec word embeddings are created using a neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window. Therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}. There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW). The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}. This is illustrated in figure~\ref{figure:word2vecModels}, in this figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words. \citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach. Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.
\begin{figure}[hbt]
\includegraphics[width=4in]{Plots/Model-Architecture-of-CBOW-and-Skip-Gram.png}
\caption{Illustration of the CBOW and Skip-Gram models, as presented by \citet{chen2017convolutional}}\label{figure:word2vecModels}
\end{figure}
\FloatBarrier
\subsubheader{Paragraph vectors}
Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector in their paper "Distributed representations of sentences and documents". The Paragraph Vector framework is based on the word vectors framework. The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses a matrix, which consists of every paragraph. This matrix is used to replace a concatenation or average of word vectors. An advantage of the paragraph vector model is that it takes the word order into consideration, at least in a small context \cite{le2014distributed}. \citet{dai2015document} state that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on Wikipedia and arXiv texts.

@@

\subsubheader{TF-IDF}
Term Frequency * Inverted Document Frequency (TF-IDF) is a method that does not rely on a neural network and, therefore, does not require training. The TF-IDF score is the product of the term frequency in a text and the inverted document frequency of the same term in a corpus of texts. Both of which can be calculated in a variety of ways. Figure~\ref{table:TFIDFScore} shows an example of the TF-IDF calculation. The multiplication of the TF and IDF is referred to as the TF-IDF score. The text, provided to the algorithm, is analyzed on word occurrences on corpus and document level, this results in a score per word. This score can be converted to a feature vector, in which the indexes of this vector represent the words and the value is the TF-IDF score. The size of this feature vector can optionally be controlled by hashing the words in the text, which can then be reduced to a given size. If this is not applied, the size of the feature vector is equal to the number of unique words in the corpus, also known as the (corpus) vocabulary.  The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences. Some applications of this technique limit the number of unique words in the text supplied to the TF-IDF algorithm, they do this by taking only a certain amount of top words, ordered on their occurrence. This reduces the amount of storage needed when hashing is not applied. It furthermore reduces the number of words which occur rarely. Due to the nature of TF-IDF, these rare words have a high score, cancelling out other more frequent words, while rarely occurring in the corpus.
\vspace{0.3in}\begin{table}[hbt]
\begin{center}
\begin{tabular}{|p{1in}|p{1in}|p{1in}|p{1.3in}|p{1in}|}
\hline
Term & Frequency (TF) & Document Frequency (DF) & Inverted Document Frequency (IDF) & TF-IDF score\\
\hline
Exponential & 4 & 15 & 0.824 & 3.296\\
\hline
Occurrence & 1 & 20 & 0.699 & 0.699\\
\hline
Multitude & 1 & 40 & 0.398 & 0.398\\
\hline
Abstract & 100 & 100 & 0 & 0\\
\hline
\end{tabular}
\caption{Example of TF-IDF score calculation.}\label{table:TFIDFScore}
\end{center}
\end{table}
\FloatBarrier
\end{jumpin}
As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", that all embedding methods rely on the same hypothesis, \textit{words that occur in similar contexts have similar meanings}. They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained has more influence on this than the corpus size.

\subheader{Validation methods}
The results produced by the previously mentioned techniques have to be validated to determine their quality (in usage). The quality of the results can be validated through various validation metrics, one of these is the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric}. The embeddings can furthermore be validated through their performance on tasks such as word analogy, word similarity, categorization and embedding visualization. These tasks can be designed to produce a score that indicates the performance on a specific task. \citet{schnabel2015evaluation} found that a single validation metric cannot produce a representative result for other tasks. Embeddings that perform well on one task do not have to perform well on another task. As a result, findings about the performance of an embedding method are limited to the task on which they are tested. Their results cannot be generalized to state that the embeddings are overall "performing well". Validation tasks use either labeled or unlabeled data. Labeled data is data that is in some way marked so that the correct answer can be derived from it, while this is not possible with unlabelled data. Labeled data enables the use of unsupervised learning models since  \textit{a system or model which is not involved in the actual learning} can automatically validate the given results and use it as feedback for the next learning iteration. Unlabelled data, on the other hand, requires human interaction to give a score for the produced result. The validation tasks can also be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task and Intrinsic evaluation, which directly tests the relationships of the word embedding themselves. \citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations since the performance on downstream tasks is not consistent across tasks.

@@

Since the word embeddings are created form a given text, these embeddings are bound to the text. All meaning embedded in the word embedding is derived from the original text. Because of this, embeddings can be "Domain-specific" meaning that it only knows words (or a specific word) in a certain context. This becomes most clear when faced with words that can have different meanings in different contexts. For this research, we categorize the embeddings into two categories, generic embeddings and domain-specific embeddings. The generic embeddings are trained on a collection of texts that use common English and contains a wide variety of topics. The domain-specific embeddings are trained on a collection of texts that uses uncommon English (i.e., domain-specific terms) or is limited to a small number of topics. Given these terms, we regard the embeddings trained on the Wikipedia corpus\cite{lai2016generate, pennington2014glove, dai2015document, lau2016empirical, schnabel2015evaluation} as general, since Wikipedia uses common English and spans a wide range of topics. On the other hand, we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific; these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus. Figure~\ref{figure:domainPlot} illustrates our corpus, marked in green, in comparison to the Wikipedia corpus, marked in blue. Our corpus is a collection of domain specific texts, written in academic language. A set that would be more specific would only focus on the individual domains or sub-domains.

>>>>

\subheader{Neural Network}
A complete in-depth background into neural networks is beyond the scope of this thesis, therefore we will only describe the simplified working of a neural network and its basic application in IR.
Neural Networks are multi-layered computational software, based on matrix transformations, which tries to map input values to output values. This mapping uses a pre-defined amount of layers that modify the values through matrix transformations. Neural networks rely on training to create optimal values for these layers. Finding these optimal values is done iteratively, via a process known as "back-propogation". Back-propogation is done by starting at the output layer of the Neural Network and tracing error in the output back through the layers. This error information is used to improve the values of the layers. The values in the layers are only changed at training time; high-quality training data is therefore essential for neural networks. Neural networks can be applied to many different tasks, as long as there is sufficient training data available. The training is the process of iteratively adjusting multiplication matrices or vectors to achieve the optimal result. Which is the result that is as close as possible to the given output for all input and output sets, without under performing on other sets\footnote{Having only good results for the training/validation set is know as overfitting. This means that the layer-values are fine-tuned to only perform (extremely) well on one set, while under performing on others}.\\Neural Networks are used, in the creation of word embeddings, to either predict words that may occur around a given word or predict a word given words that surround it. For example, given the sentence\\
\begin{center}
\textit{"The quick brown fox jumps over the lazy dog"}
\end{center}
the Neural Network can be trained to either predict the words around "jumps", which we refer to as context words (the, quick, brown, fox, over, the, lazy, dog). It can also predict the word "jumps", given the context words (the, quick, brown, fox, over, the, lazy, dog). This result in a matrix, a vector per word which is referred to as a word embedding. This embedding indicates "word relatedness" which, as mentioned earlier enables association (thus retrieval) with related(relevant) texts. It is to be noted that the word embeddings are only able to represent word relatedness to the other words trained in the same run. Due to the random initialization of the initial values of the layers in the neural networks, neural networks do not produce every run the same results. Therefore, word embeddings from different runs of the same neural network cannot be compared.

@@

\subheader{Text analysis techniques}
To enable a computer to process text, for embedding creation or other tasks, the text has to be processed by an algorithm. In this research, we used embeddings created by Word2Vec and TF-IDF feature vectors.
\begin{jumpin}
\subsubheader{Word2Vec}
Word2vec word embeddings are created using a neural network, Word2vec learns word embeddings via maximizing the log conditional probability of the word given the context word(s) occurring within a fixed-sized window. Therefore the learned embeddings contain useful knowledge about word co-occurrence\cite{nalisnick2016improving}. There are multiple input/output possibilities for the neural network, best known are Skip-gram and the Continuous Bag-of-Words model (CBOW). The Skip-gram model takes a target word as input and outputs the predicted output words, while CBOW takes the context words as input and outputs the predicted target word\cite{nalisnick2016improving, pennington2014glove}. This is illustrated in Figure~\ref{figure:word2vecModels}, in this figure, $v(w)$ represents the target word, and $v(w...)$ represent the context words. \citet{mikolov2013distributed}\cite{mikolov2013efficient} presented several extensions to the word2vec model that improve the quality of vector training and its speed, such as introducing Hierarchical Softmax, Negative Sampling and the subsampling of frequent words to the Skip-gram approach. Variations to the word2vec model have also been proposed, such as the doc2vec model described by \citet{lau2016empirical} which creates document embeddings instead of word embeddings.
\begin{center}
\begin{figure}[hbt]
\includegraphics[width=4in]{Plots/Model-Architecture-of-CBOW-and-Skip-Gram.png}
\caption{Illustration of the CBOW and Skip-Gram models, as presented by \citet{chen2017convolutional}. Left part of the Figure illustrates the CBOW model, context words are represented at the left side (input) and the center word (output) is represented as $v(w)$ as output. The right side of the Figure illustrates the Skip-Gram Model, which takes the center word as input (left) and outputs the context words (right).}\label{figure:word2vecModels}
\end{figure}
\FloatBarrier
\end{center}
\subsubheader{Paragraph vectors}
Variations on the word2vec model have also been proposed,~\citet{le2014distributed} introduced the paragraph vector in their paper "Distributed representations of sentences and documents". The Paragraph Vector framework is based on the word vectors framework. The difference between the frameworks is the calculation of the probability, the Paragraph Vector framework uses a matrix, which consists of every paragraph. This matrix is used to replace a concatenation or average of word vectors. An advantage of the paragraph vector model is that it takes the word order into consideration, at least in a small context \cite{le2014distributed}. \citet{dai2015document} state that the Paragraph Vectors model performs significantly better than other models on grouping, triplet finding and related object/article finding tasks on Wikipedia and arXiv texts.

@@

\subsubheader{TF-IDF}
Term Frequency * Inverted Document Frequency (TF-IDF) is a method that does not rely on a neural network and, therefore, does not require training. The TF-IDF score is the product of the term frequency in a text and the inverted document frequency of the same term in a corpus of texts. Both of which can be calculated in a variety of ways. Table~\ref{table:TFIDFScore} shows an example of the TF-IDF calculation. The multiplication of the TF and IDF is referred to as the TF-IDF score. The text, provided to the algorithm, is analyzed on word occurrences on corpus and document level, this results in a score per word. This score can be converted to a feature vector, in which the indexes of this vector represent the words and the value is the TF-IDF score. The size of this feature vector can optionally be controlled by hashing the words in the text, which can then be reduced to a given size. If this is not applied, the size of the feature vector is equal to the number of unique words in the corpus, also known as the (corpus) vocabulary.  The feature vectors produced by TF-IDF do not capture syntactic or semantic information about words, but capture information about word occurrences. Some applications of this technique limit the number of unique words in the text supplied to the TF-IDF algorithm, they do this by taking only a certain amount of top words, ordered on their occurrence. This reduces the amount of storage needed when hashing is not applied. It furthermore reduces the number of words which occur rarely. Due to the nature of TF-IDF, these rare words have a high score, cancelling out other more frequent words, while rarely occurring in the corpus.
\vspace{0.3in}\begin{table}[hbt]
\begin{center}
\begin{tabular}{|p{1in}|p{1in}|p{1in}|p{1.3in}|p{1in}|}
\hline
Term & Frequency (TF) & Document Frequency (DF) & Inverted Document Frequency (IDF) & TF-IDF score\\
\hline
Exponential & 4 & 15 & 0.824 & 3.296\\
\hline
Occurrence & 1 & 20 & 0.699 & 0.699\\
\hline
Multitude & 1 & 40 & 0.398 & 0.398\\
\hline
Abstract & 100 & 100 & 0 & 0\\
\hline
\end{tabular}
\caption{Example of TF-IDF score calculation.}\label{table:TFIDFScore}
\end{center}
\end{table}
\FloatBarrier
\end{jumpin}
As \citet{lai2016generate} state in their paper "How to generate a good word embedding?", that all embedding methods rely on the same hypothesis, \textit{words that occur in similar contexts have similar meanings}. They furthermore found that larger corpus' lead to better quality embeddings, but that the domain in which the embeddings are trained has more influence on this than the corpus size.

\subheader{Validation methods}
The results produced by the previously mentioned techniques have to be validated to determine their quality (in usage). The quality of the results can be validated through various validation metrics, one of these is the F1 score\footnote{The F1 score combines the precision score and the recall score in a single metric}. The embeddings can furthermore be validated through their performance on tasks such as word analogy, word similarity, categorization and embedding visualization. These tasks can be designed to produce a score that indicates the performance on a specific task. \citet{schnabel2015evaluation} found that a single validation metric cannot produce a representative result for other tasks. Embeddings that perform well on one task do not have to perform well on another task. As a result, findings about the performance of an embedding method are limited to the task on which they are tested. Their results cannot be generalized to state that the embeddings are overall "performing well". Validation tasks use either labeled or unlabeled data. Labeled data is data that is in some way marked so that the correct answer can be derived from it, while this is not possible with unlabelled data. The validation tasks can be divided into two groups, extrinsic evaluation, ones that use word embeddings as input for a downstream task and Intrinsic evaluation, which directly tests the relationships of the word embedding themselves. \citet{schnabel2015evaluation} note that the extrinsic evaluation may not be consistent with intrinsic evaluations since the performance on downstream tasks is not consistent across tasks.

@@

Since the word embeddings are created form a given text, these embeddings are bound to the text. All meaning embedded in the word embedding is derived from the original text. Because of this, embeddings can be "Domain-specific" meaning that it only knows words (or a specific word) in a certain context. This becomes most clear when faced with words that can have different meanings in different contexts. For this research, we categorize the embeddings into two categories, generic embeddings and domain-specific embeddings. The generic embeddings are trained on a collection of texts that use common English and contains a wide variety of topics. The domain-specific embeddings are trained on a collection of texts that uses jargon English (i.e., domain-specific terms) or is limited to a small number of topics. Given these terms, we regard the embeddings trained on the Wikipedia corpus\cite{lai2016generate, pennington2014glove, dai2015document, lau2016empirical, schnabel2015evaluation} as general, since Wikipedia uses common English and spans a wide range of topics. On the other hand, we regard the embeddings created by \citet{Truong2017Thesis} as Domain specific; these embeddings were created on academic articles, which use domain-specific terms and notations and only consists of academic texts, which contains less general/generic words compared to the Wikipedia corpus. Figure~\ref{figure:domainPlot} illustrates our corpus, marked in green, in comparison to the Wikipedia corpus, marked in blue. Our corpus is a collection of domain specific texts, written in academic language. A set that would be more specific would only focus on the individual domains or sub-domains.

### 2018-07-02 Thesis/Parts/Data/Data.tex
Auto stash before merge of "master" and "origin/master"

We use the median rank to indicate at which rank the 'standard' article would be ranked, based on its title or abstract. We do this by taking the median of the respective rank from each article. This gives us an indication of the behaviour of the articles in our validation set. This median rank (mostly) ignores the outliers, we therefore also use the average rank, which gives a more global indication, although this rank may be over-influenced by some outliers.

>>>>

The median rank of a journal indicates the point where 50\% of all articles are to the left of a virtual line and 50\% are to the right of this line. The median rank therefore indicates the position of the "normal/typical"  article. This median rank differs from the average, since the median is not influenced by a single value. If the median is 20, it does not matter if an article is 25 of 250, it does matter however if an articles is 19 or 21. For the average this is not the case, the average is influenced by single articles. Therefore it does not represents the "normal/typical" article but it represents the exact average of all articles in the validation set, which is changed when an article changed from 25 to 250.\\
We use the median rank to indicate at which rank the typical article would be ranked, based on its title and abstract. We do this by taking the median of the respective rank from each article. This gives us an indication of the behaviour of the articles in our validation set. We also calculate the average score for the title and abstract of all articles. This gives us four scores: median title rank, median abstract rank, average title rank \& average abstract rank.\\

### 2018-07-02 Thesis/Parts/Discussion/Discussion.tex
Auto stash before merge of "master" and "origin/master"

\documentclass[../../Thesis.tex]{subfiles}
\externaldocument{../Research_results/Research_results}
\externaldocument{../Data/Data}
\begin{document}
\header{Discussion}
\subheader{Result analysis}
\begin{jumpin}
\subsubheader{Best performers}
The data, as presented in figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles. For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings, which 1 median rank higher on the abstracts, and equal on the titles.

\subsubheader{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title. The main difference between the abstract \& title is that the title contains fewer tokens compared to the abstract (see table~\ref{table:corpusSize}). This means that the titles contain less information than the abstracts. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles. The TF-IDF method works better on the abstract, which contain more tokens, which improves the differentiating the different abstract. The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case. It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not look into this further due to our findings that the TF-IDF performance stagnates (presented in figure~\ref{figure:tfidfPerformance}).

\subsubheader{Limited TF-IDF embeddings}
The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding (which does not have a limited vocabulary), on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results; higher vocabulary sizes give better performance. However, figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. Their pattern shows a decent performance indicates the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.\\This seems to indicate that the cut-off was effective, but that it did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings. Resulting in high median and average ranks, and in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However, they can be processed more efficiently during calculations}. This results in a lower memory requirement.

@@

\subsubheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding. The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in figure~\ref{figure:tfidfPerformance}). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is significantly worse than the embedding, which also uses less memory. This indicates that the embeddings are able to store the relatedness information more densely than the TF-IDF feature vectors can store the worod occurrence information.

\subsubheader{Journal plots}
Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the journals in the, what we will refer to as "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journals, grouped with k-means on the original 300-dimensional embedding vector. In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together. 
The interactive version shows that the clusterings, as seen on all four figures, are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. It furthermore shows that the k-means groupings give insight in research fields, although it is limited by the number of groups the k-means algorithm creates. Our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles. The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human-made) partitioning data. They have therefore a more reliable grouping metric.
\end{jumpin}
\subheader{Improvements}
This research shows that even tough the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings on the abstracts. Earlier research already proposed improvements to the word embeddings. \citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative. While this looks promising, we have to keep in mind that our task differs from earlier tasks. We do not categorize on two categories but more than 3k. Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale, which complicates the task due to the "grey areas"  between categories. These are the area's in which the classification algorithm is "in doubt" and could reasonably assing the article to both journals. The number of these grey areas increases given more categories. \citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task. \citet{wang2016linked} introduced the Linked Document Embedding method (LDE) method, which makes use of additional information about a document, such as citations. Their research specifically focused on categorizing documents, showed a 5.89\% increase of the micro-F1 score on LDE compared to CBOW, and a 9.11\% increase of the macro-F1 score. We would expect that applying this technique to our dataset would improve our scores, given earlier results on comparable tasks.\\
Even though much research has been done, we have not been able to find published results which are directly comparable to our results. This is likely due to our high amount of categorization groups, which enabled us to handle our results as a ranking problem, instead of an absolute hit, which has been used in earlier researches\cite{wang2016linked}. Even though we have an F1 score, which indicates performance on the absolute hits, our results are not comparable to other works due to the number of categories, and their overlapping subjects\footnote{As visualized in the journal embedding plots and discussed earlier}.

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\externaldocument{../Research_results/Research_results}
\externaldocument{../Data/Data}
\begin{document}
\header{Discussion}
In this chapter, the results presented in Chapter 6: Results will be discussed. No additional results will be presented in this chapter.
\subheader{Result analysis}

\subsubheader{Best performers}
The data, as presented in Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} shows that the 10k/10k set performs better than all other TF-IDF sets, although the difference with the 5k/10k is low, 1  median rank on abstract and 3 median ranks on the titles. For the embeddings, the TF-IDF weighted embedding works better than the others, although it is not a significant improvement (1 rank on a set of more than 3.000) compared to the default embeddings, which 1 median rank higher on the abstracts, and equal on the titles.

\subsubheader{TF-IDF}
The TF-IDF feature vectors outperform the embeddings on the abstract, while the embeddings outperform the TF-IDF feature vectors on the title. The main difference between the abstract \& title is that the title contains fewer tokens compared to the abstract (see Table~\ref{table:corpusSize}). This means that the titles contain less information than the abstracts. Due to this, the TF-IDF method, which is purely based on word-occurrences \& counts has less information on the titles. The TF-IDF method works better on the abstract, which contain more tokens, which improves the differentiating the different abstract. The data furthermore shows that increasing the vocabulary size increases the performance of the TF-IDF, this means that none of the created cut-off's resulted in cutting off noise, the increasing size of the vocabulary only improved the performance in this case. It could be possible that at higher vocabulary sizes the cut-off would result in a sharper signal, we did not look into this further due to our findings that the TF-IDF performance stagnates (presented in Figure~\ref{figure:tfidfPerformance}).
\clearpage
\subsubheader{Limited TF-IDF embeddings}
The limited TF-IDF embeddings all underperform, compared to the TF-IDF embedding (which does not have a limited vocabulary), on the median and average ranking. Indicating that the noise reduction is too much, and it removes meaningful words. If the noise reduction would be too low, we would only see a slight increase or none at all. However, the rank lowers, indicating the reduction in embedding quality due to missing words. This is in line with what we found with the TF-IDF results; higher vocabulary sizes give better performance. 
\begin{jumpin}
\subsubsubheader{Rank distribution}
However, Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show that their rank distribution is different from the other embeddings. Their pattern shows a decent performance indicates the following pattern: a high/average performance on the top-rankings, an underperformance on the middle rankings and a resulting stack-up of articles with a high-ranking. This is further supported by the TF-IDF score on titles (Figure~\ref{figure:titleRanks}), on which the limited TF-IDF embeddings are the top performance. Indicating a better performance on the top-1 articles compared to the other sets.
\end{jumpin}This seems to indicate that the cut-off was effective, but that it did not suit our purpose. The cut-off moved the "middle-ranked"  articles to either the higher end or the lower end of the rankings. Resulting in high median and average ranks, and in (relatively) high accuracy scores. The reduction in vocabulary size did not reduce the storage size for the embeddings, except for the 1K-6K embedding. This indicates that only the 1K-6K cut actually removes entire titles and abstracts, since all vectors are stored as dense-vectors\footnote{Dense vectors are bigger in memory, since they store all their values, including zeros. However, they can be processed more efficiently during calculations}. This results in a lower memory requirement.

@@

\subsubheader{Memory usage}
Although the TF-IDF outperforms the embeddings on the abstracts, the memory usage of the TF-IDF is higher than the memory usage of the embeddings. The top-performing embedding, TF-IDF weighted embedding, uses 3.13 GB, the top performing TF-IDF, 10K/10K uses 11.61 GB, which is 270.93\% of the storage size needed for the embedding. The closest TF-IDF configuration we used was 1K/1K, which uses 5.13 GB (as displayed in Figure~\ref{figure:tfidfPerformance}). This TF-IDF set has a median title rank of 183 and a median abstract rank of 44. Which is significantly worse than the embedding, which also uses less memory. This indicates that the embeddings are able to store the relatedness information more densely than the TF-IDF feature vectors can store the worod occurrence information.

\subsubheader{Journal plots}
Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the journals in the, what we will refer to as "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journals, grouped with k-means on the original 300-dimensional embedding vector. In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together. 
The interactive version shows that the clusterings, as seen on all four figures, are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. It furthermore shows that the k-means groupings give insight in research fields, although it is limited by the number of groups the k-means algorithm creates. Our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles. The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human-made) partitioning data. They have therefore a more reliable grouping metric.

\subheader{Improvements}
This research shows that even tough the embeddings can capture and preserve relatedness, TF-IDF is able to outperform the embeddings on the abstracts. Earlier research already proposed improvements to the word embeddings. \citet{dai2015document} show that the usage of paragraph vectors improve the accuracy of word embeddings with 4.4\% on triplet creation with the Wikipedia corpus and a 3.9\% improvement on the same task based on the arXiv articles.\\
Furthermore, \citet{le2014distributed} show that the usage of paragraph vectors decrease the error rate (positive/negative) with 7.7\% compared to averaging the word embeddings on categorizing text as either positive or negative. While this looks promising, we have to keep in mind that our task differs from earlier tasks. We do not categorize on two categories but more than 3k. Still, we would expect an improvement by using paragraph vectors since the classification task if fundamentally the same, only on a much larger scale, which complicates the task due to the "grey areas"  between categories. These are the area's in which the classification algorithm is "in doubt" and could reasonably assing the article to both journals. The number of these grey areas increases given more categories. \citet{pennington2014glove} showed that the GloVe model outperforms the CBOW model, which is used in this research, on a word analogy task. \citet{wang2016linked} introduced the Linked Document Embedding method (LDE) method, which makes use of additional information about a document, such as citations. Their research specifically focused on categorizing documents, showed a 5.89\% increase of the micro-F1 score on LDE compared to CBOW, and a 9.11\% increase of the macro-F1 score. We would expect that applying this technique to our dataset would improve our scores, given earlier results on comparable tasks.\\
Even though much research has been done, we have not been able to find published results which are directly comparable to our results. This is likely due to our high amount of categorization groups, which enabled us to handle our results as a ranking problem, instead of an absolute hit, which has been used in earlier researches\cite{wang2016linked}. Even though we have an F1 score, which indicates performance on the absolute hits, our results are not comparable to other works due to the number of categories, and their overlapping subjects\footnote{As visualized in the journal embedding plots and discussed earlier}.
